Novelty Detection for Semantic Place Categorization

### 2011-07-14 thesis/introduction.tex
little typo

% Machine-representations are not useful to solve the required problem.
One may argue that robots and computers can already represent and understand environments, but they
do so by using representations that are not human friendly: e.g.\ a robot can uniquely identify the
location of a certain landmark using internal coordinates, but those coordinates are not understandable
for humans. A robot may be able to detect a tag placed on an object, but such an approach does not scale
outsize structured environments: new objects are created everyday, there is huge amount of already
existing objects and concepts by their nature are dynamic. For this reason, methods need 
to be developed that will allow robots to represent real-world environments and allow human concepts
to be transferred into the robot representations.

>>>>

% Machine-representations are not useful to solve the required problem.
One may argue that robots and computers can already represent and understand environments, but they
do so by using representations that are not human friendly: e.g.\ a robot can uniquely identify the
location of a certain landmark using internal coordinates, but those coordinates are not understandable
for humans. A robot may be able to detect a tag placed on an object, but such an approach does not scale
outside structured environments: new objects are created everyday, there is huge amount of already
existing objects and concepts by their nature are dynamic. For this reason, methods need 
to be developed that will allow robots to represent real-world environments and allow human concepts
to be transferred into the robot representations.
